---
title: "10_heatmap"
author: "Heekuk"
date: "2025-08-08"
output: html_document
---

### g)  Supervised Heatmap {.tabset}

This analysis visualizes biological profiles that show differential patterns across predefined sample groups. A heatmap is generated using selected features based on statistical filtering, with sample groupings annotated for comparison. Color intensity reflects normalized feature values, enabling interpretation of group-specific patterns and biologically relevant differences.

```{r SupervisedHeatmap, include=FALSE}
  convert_and_include_pdf <- function(tool, index, subgroup = NULL, da_wd, da_com) {
    pattern <- sprintf("%s.*\\(%s\\)%s.*\\.pdf$",tool,  da_com[index], ifelse(is.null(subgroup), "", paste0(".*", subgroup)))
    input_pdf <- list.files(path = da_wd, pattern = pattern, full.names = TRUE)
    
    if(length(input_pdf) == 0) {
      message("No PDF files found for pattern: ", pattern)
      return()
    }
    
    if (length(input_pdf) > 1) {
    
      message("Multiple PDF files matched pattern: ", pattern, " - using the first: ", basename(input_pdf[1]))
    
    }
    
    base_name <- tools::file_path_sans_ext(basename(input_pdf[1]))
    output_png <- file.path(dirname(input_pdf[1]), paste0(base_name, ".png"))
    
    image_read_pdf(input_pdf[1], pages = 1) %>%
      image_convert(format = "png") %>%
      image_write(output_png)
    
    include_graphics(output_png)
  }


```


```{r SupervisedHeatmap_title1, echo=FALSE, results='asis', eval=!is.na(imgInfo$shplot[1])}
if(!is.na(imgInfo$shplot[1])) {
  cat("#### ", imgInfo$shplot[1], " {.tabset}", "\n", sep="")
}
```



```{r SH_1, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$shplot[1]) && any(grepl(sprintf("heatmap.*\\(%s\\)%s.*\\.pdf$", imgInfo$shplot[1], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("heatmap",1, subgroup, dirInfo$image.wd, imgInfo$shplot)
```



```{r SupervisedHeatmap_title2, echo=FALSE, results='asis', eval=!is.na(imgInfo$shplot[2])}
if(!is.na(imgInfo$shplot[2])) {
  cat("#### ", imgInfo$shplot[2], " {.tabset}", "\n", sep="")
}
```

```{r SH_2, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$shplot[2]) && any(grepl(sprintf("heatmap.*\\(%s\\)%s.*\\.pdf$", imgInfo$shplot[2], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("heatmap",2, subgroup, dirInfo$image.wd, imgInfo$shplot)
```




```{r SupervisedHeatmap_title3, echo=FALSE, results='asis', eval=!is.na(imgInfo$shplot[3])}
if(!is.na(imgInfo$shplot[3])) {
  cat("#### ", imgInfo$shplot[3], " {.tabset}", "\n", sep="")
}
```

```{r SH_3, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$shplot[3]) && any(grepl(sprintf("heatmap.*\\(%s\\)%s.*\\.pdf$", imgInfo$shplot[3], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("heatmap",3, subgroup, dirInfo$image.wd, imgInfo$shplot)
```


```{r SupervisedHeatmap_title4, echo=FALSE, results='asis', eval=!is.na(imgInfo$shplot[4])}
if(!is.na(imgInfo$shplot[4])) {
  cat("#### ", imgInfo$shplot[4], " {.tabset}", "\n", sep="")
}
```

```{r SH_4, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$shplot[4]) && any(grepl(sprintf("heatmap.*\\(%s\\)%s.*\\.pdf$", imgInfo$shplot[4], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("heatmap",4, subgroup, dirInfo$image.wd, imgInfo$shplot)
```



```{r SupervisedHeatmap_title5, echo=FALSE, results='asis', eval=!is.na(imgInfo$shplot[5])}
if(!is.na(imgInfo$shplot[5])) {
  cat("#### ", imgInfo$shplot[5], " {.tabset}", "\n", sep="")
}
```

```{r SH_5, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$shplot[5]) && any(grepl(sprintf("heatmap.*\\(%s\\)%s.*\\.pdf$", imgInfo$shplot[5], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("heatmap",5, subgroup, dirInfo$image.wd, imgInfo$shplot)
```



