---
title: "5_2_ancom2"
author: "Heekuk"
date: "2024-06-09"
output: html_document
---

### e)  Differential Abundance Analysis {.tabset}

Differential abundance testing (ANCOMBC an R package) were carried out to determine taxa differences between groups. Here, we identified a small number of bacterial ASVs that differed between the baseline and the other group(s). Significantly differential abundant bacteria were determined by p < 0.05 (open circle) and padj (FDR) < 0.05 (close circle)  from both tests.


```{r DA, include=FALSE}
  convert_and_include_pdf <- function(tool, index, subgroup = NULL, da_wd, da_com) {
    pattern <- sprintf("%s.*\\(%s\\)%s.*\\.pdf$",tool,  da_com[index], ifelse(is.null(subgroup), "", paste0(".*", subgroup)))
    input_pdf <- list.files(path = da_wd, pattern = pattern, full.names = TRUE)
    
    if(length(input_pdf) == 0) {
      cat("No PDF files found for pattern:", pattern, "\n")
      return()
    }
    
    base_name <- tools::file_path_sans_ext(basename(input_pdf[1]))
    output_png <- file.path(dirname(input_pdf[1]), paste0(base_name, ".png"))
    
    image_read_pdf(input_pdf[1], pages = 1) %>%
      image_convert(format = "png") %>%
      image_write(output_png)
    
    include_graphics(output_png)
  }
```

```{r conditional-title_1, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[1])}
if(!is.na(imgInfo$daplot[1])) {
  cat("#### ", imgInfo$daplot[1], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN1, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[1])}
if(!is.na(imgInfo$daplot[1])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_1, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[1])}
convert_and_include_pdf("ancom2",1, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_2, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2])}
if(!is.na(imgInfo$daplot[2])) {
  cat("#### ", imgInfo$daplot[2], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN2, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2])}
if(!is.na(imgInfo$daplot[2])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_2, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[2])}
convert_and_include_pdf("ancom2",2, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_3, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2])}
if(!is.na(imgInfo$daplot[3])) {
  cat("#### ", imgInfo$daplot[3], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN3, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[3])}
if(!is.na(imgInfo$daplot[3])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_3, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[3])}
convert_and_include_pdf("ancom2",3, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_4, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[4])}
if(!is.na(imgInfo$daplot[4])) {
  cat("#### ", imgInfo$daplot[4], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN4, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[4])}
if(!is.na(imgInfo$daplot[4])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_4, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[4])}
convert_and_include_pdf("ancom2",4, subgroup, dirInfo$da.wd, imgInfo$daplot)
```


```{r conditional-title_5, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[5])}
if(!is.na(imgInfo$daplot[5])) {
  cat("#### ", imgInfo$daplot[5], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN5, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[5])}
if(!is.na(imgInfo$daplot[5])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_5, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[5])}
convert_and_include_pdf("ancom2",5, subgroup, dirInfo$da.wd, imgInfo$daplot)
```


```{r conditional-title_6, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[6])}
if(!is.na(imgInfo$daplot[6])) {
  cat("#### ", imgInfo$daplot[6], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN6, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[6])}
if(!is.na(imgInfo$daplot[6])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_6, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[6])}
convert_and_include_pdf("ancom2",6, subgroup, dirInfo$da.wd, imgInfo$daplot)
```


```{r conditional-title_7, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[7])}
if(!is.na(imgInfo$daplot[7])) {
  cat("#### ", imgInfo$daplot[7], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN7, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[7])}
if(!is.na(imgInfo$daplot[7])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_7, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[7])}
convert_and_include_pdf("ancom2",7, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_8, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[8])}
if(!is.na(imgInfo$daplot[8])) {
  cat("#### ", imgInfo$daplot[8], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN8, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[8])}
if(!is.na(imgInfo$daplot[8])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_8, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[8])}
convert_and_include_pdf("ancom2",8, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_9, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[9])}
if(!is.na(imgInfo$daplot[9])) {
  cat("#### ", imgInfo$daplot[9], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN9, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[9])}
if(!is.na(imgInfo$daplot[9])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_9, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[9])}
convert_and_include_pdf("ancom2",9, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_10, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[10])}
if(!is.na(imgInfo$daplot[10])) {
  cat("#### ", imgInfo$daplot[10], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_AN10, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[10])}
if(!is.na(imgInfo$daplot[10])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_10, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='70%', eval=!is.na(imgInfo$daplot[10])}
convert_and_include_pdf("ancom2",10, subgroup, dirInfo$da.wd, imgInfo$daplot)
cat("***","\n", sep="")
```
