---
title: "5_1_DA"
author: "Heekuk"
date: "2024-06-09"
output: html_document
---

### e)  Differential Abundance Analysis {.tabset}

Differential abundance testing was carried out to determine taxa differences between groups. Here, we identified a small number of bacterial ASVs that differed between the baseline and the other group(s). Significantly differentially abundant bacteria were determined by p < 0.05 (open circle) and padj (FDR) < 0.05 (closed circle) from both tests. 

The tests are only provided for comparisons that can be performed.


```{r DA, include=FALSE}
  regex_escape <- function(x) {
    gsub("([+()\\[\\].*?^$|{}\\\\])", "\\\\\\1", x, perl = TRUE)
  }
  .daw <- function(i, default = "70%") {
    w <- imgInfo$daplot_width
    if (!is.null(w) && length(w) >= i && !is.na(w[i])) w[i] else default
  }

  convert_and_include_pdf <- function(tool, index, subgroup = NULL, da_wd, da_com) {
    safe_token <- regex_escape(da_com[index])
    pattern <- sprintf("%s.*\\(%s\\)%s.*\\.pdf$", tool, safe_token, ifelse(is.null(subgroup), "", paste0(".*", subgroup)))
    input_pdf <- list.files(path = da_wd, pattern = pattern, full.names = TRUE)
    
    if(length(input_pdf) == 0) {
      cat("No PDF files found for pattern:", pattern, "\n")
      return()
    }
    
    base_name <- tools::file_path_sans_ext(basename(input_pdf[1]))
    output_png <- file.path(dirname(input_pdf[1]), paste0(base_name, ".png"))
    
    image_read_pdf(input_pdf[1], pages = 1) %>%
      image_convert(format = "png") %>%
      image_write(output_png)
    
    include_graphics(output_png)
  }

# Differential abundance testing (DESeq2, ANCOMBC, ZicoSeq R package) was carried out to determine taxa differences between groups. Here, we identified a small number of bacterial ASVs that differed between the baseline and the other group(s). Significantly differentially abundant bacteria were determined by p < 0.05 (open circle) and padj (FDR) < 0.05 (closed circle) from both tests. For the ZicoSeq plot, random effects were controlled by treating the recorded ID as a longitudinal study. The plot shows padj (FDR) < 0.05 with their intensity of prevalence. The tests are only provided for comparisons that can be performed.


```


```{r conditional-title_1, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[1])}
if(!is.na(imgInfo$daplot[1])) {
  cat("#### ", imgInfo$daplot[1], " {.tabset}", "\n", sep="")
}
```


```{r conditional-title_D1, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[1])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_1, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(1), eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",1, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_Al1, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[1])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_1, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(1), eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",1, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN1, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[1])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_1, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(1), eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",1, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc1, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[1])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_1, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(1), eval=!is.na(imgInfo$daplot[1]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",1, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_2, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2])}
if(!is.na(imgInfo$daplot[2])) {
  cat("#### ", imgInfo$daplot[2], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D2, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[2])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_2, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(2), eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",2, subgroup,dirInfo$da.wd, imgInfo$daplot)
```


```{r conditional-title_Al2, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[2])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_2, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(2), eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",2, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN2, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[2])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_2, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(2), eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",2, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc2, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[2])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_2, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(2), eval=!is.na(imgInfo$daplot[2]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[2]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",2, subgroup, dirInfo$da.wd, imgInfo$daplot)
```


```{r conditional-title_3, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[2])}
if(!is.na(imgInfo$daplot[3])) {
  cat("#### ", imgInfo$daplot[3], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D3, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[3])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_3, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(3), eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",3, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_Al3, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[3])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_3, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(3), eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",3, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN3, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[3])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_3, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(3), eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",3, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc3, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[2])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_3, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(3), eval=!is.na(imgInfo$daplot[3]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[3]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",3, subgroup, dirInfo$da.wd, imgInfo$daplot)
```



```{r conditional-title_4, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[4])}
if(!is.na(imgInfo$daplot[4])) {
  cat("#### ", imgInfo$daplot[4], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D4, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[4]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[4])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_4, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(4), eval=!is.na(imgInfo$daplot[4]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",4, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_Al4, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[4])  && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[4])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_4, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(4), eval=!is.na(imgInfo$daplot[4]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",4, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN4, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[4]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[4])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_4, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(4), eval=!is.na(imgInfo$daplot[4]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",4, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc4, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[4]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[4])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_4, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(4), eval=!is.na(imgInfo$daplot[4]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[4]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",4, subgroup, dirInfo$da.wd, imgInfo$daplot)
```






```{r conditional-title_5, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[5])}
if(!is.na(imgInfo$daplot[5])) {
  cat("#### ", imgInfo$daplot[5], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D5, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[5])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_5, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(5), eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",5, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_Al5, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[5])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_5, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(5), eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",5, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN5, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[5])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_5, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(5), eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",5, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc5, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[5])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_5, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(5), eval=!is.na(imgInfo$daplot[5]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[5]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",5, subgroup, dirInfo$da.wd, imgInfo$daplot)
```









```{r conditional-title_6, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[6])}
if(!is.na(imgInfo$daplot[6])) {
  cat("#### ", imgInfo$daplot[6], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D6, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[6]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[6])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_6, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(6), eval=!is.na(imgInfo$daplot[6]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",6, subgroup,dirInfo$da.wd, imgInfo$daplot)
```



```{r conditional-title_Al6, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[6]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[6])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_6, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(6), eval=!is.na(imgInfo$daplot[6])  && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",6, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN6, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[6]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[6])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_6, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(6), eval=!is.na(imgInfo$daplot[6]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",6, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc6, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[6]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[6])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_6, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(6), eval=!is.na(imgInfo$daplot[6]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[6]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",6, subgroup, dirInfo$da.wd, imgInfo$daplot)
```





```{r conditional-title_7, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[7])}
if(!is.na(imgInfo$daplot[7])) {
  cat("#### ", imgInfo$daplot[7], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D7, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[7])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_7, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(7), eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",7, subgroup,dirInfo$da.wd, imgInfo$daplot)
```



```{r conditional-title_Al7, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[7])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_7, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(7), eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",7, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN7, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[7])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_7, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(7), eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",7, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc7, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[7])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_7, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(7), eval=!is.na(imgInfo$daplot[7]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[7]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",7, subgroup, dirInfo$da.wd, imgInfo$daplot)
```






```{r conditional-title_8, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[8])}
if(!is.na(imgInfo$daplot[8])) {
  cat("#### ", imgInfo$daplot[8], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D8, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[8])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_8, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(8), eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",8, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_Al8, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[8])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_8, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(8), eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",8, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN8, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[8])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_8, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(8), eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",8, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc8, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[8])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_8, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(8), eval=!is.na(imgInfo$daplot[8]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[8]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",8, subgroup, dirInfo$da.wd, imgInfo$daplot)
```






```{r conditional-title_9, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[9])}
if(!is.na(imgInfo$daplot[9])) {
  cat("#### ", imgInfo$daplot[9], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D9, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[9]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[9])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_9, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(9), eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[9]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",9, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_Al9, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[9]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[9])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_9, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(9), eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[1]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",9, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_AN9, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[9]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[9])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_9, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(9), eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[9]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",9, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_zc9, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[9]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[9])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_9, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(9), eval=!is.na(imgInfo$daplot[9]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[9]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",9, subgroup, dirInfo$da.wd, imgInfo$daplot)
```





```{r conditional-title_10, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[10])}
if(!is.na(imgInfo$daplot[10])) {
  cat("#### ", imgInfo$daplot[10], " {.tabset}", "\n", sep="")
}
```

```{r conditional-title_D10, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[10])) {
  cat("##### Deseq2")
}
```

```{r Deseq2_10, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(10), eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("deseq2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("deseq2",10, subgroup,dirInfo$da.wd, imgInfo$daplot)
```

```{r conditional-title_Al10, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[10])) {
  cat("##### Aldex2")
}
```

```{r Aldex2_10, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(10), eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("aldex2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("aldex2",10, subgroup, dirInfo$da.wd, imgInfo$daplot)

```

```{r conditional-title_AN10, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[10])) {
  cat("##### ANCOMBC")
}
```

```{r ANCOMBC_10, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(10), eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("ancom2.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ancom2",10, subgroup, dirInfo$da.wd, imgInfo$daplot)
```


```{r conditional-title_zc10, echo=FALSE, results='asis', eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
if(!is.na(imgInfo$daplot[10])) {
  cat("##### ZicoSeq")
}
```

```{r Zico_10, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width=.daw(10), eval=!is.na(imgInfo$daplot[10]) && any(grepl(sprintf("ZicoSeq.*\\(%s\\)%s.*\\.pdf$", regex_escape(imgInfo$daplot[10]), ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$da.wd)))}
convert_and_include_pdf("ZicoSeq",10, subgroup, dirInfo$da.wd, imgInfo$daplot)
```

