---
title: "8_network"
author: "Heekuk"
date: "2025-03-07"
output: html_document
---

### f)  Network Analysis {.tabset}

This analysis constructs a microbial co-occurrence network based on correlation analysis of microbial abundance across samples. The pipeline processes multiple datasets, filters significant correlations using p-values or FDR, and visualizes the network using igraph. Nodes represent microbial taxa, and edges indicate correlation strength and direction, with node size reflecting centrality measures.


```{r Network, include=FALSE}
  convert_and_include_pdf <- function(tool, index, subgroup = NULL, da_wd, da_com) {
    pattern <- sprintf("%s.*\\(%s\\)%s.*\\.pdf$",tool,  da_com[index], ifelse(is.null(subgroup), "", paste0(".*", subgroup)))
    input_pdf <- list.files(path = da_wd, pattern = pattern, full.names = TRUE)
    
    if(length(input_pdf) == 0) {
      message("No PDF files found for pattern: ", pattern)
      return()
    }
    
    if (length(input_pdf) > 1) {
    
      message("Multiple PDF files matched pattern: ", pattern, " - using the first: ", basename(input_pdf[1]))
    
    }
    
    base_name <- tools::file_path_sans_ext(basename(input_pdf[1]))
    output_png <- file.path(dirname(input_pdf[1]), paste0(base_name, ".png"))
    
    image_read_pdf(input_pdf[1], pages = 1) %>%
      image_convert(format = "png") %>%
      image_write(output_png)
    
    include_graphics(output_png)
  }


```


```{r Net-title_1, echo=FALSE, results='asis', eval=!is.na(imgInfo$ntplot[1])}
if(!is.na(imgInfo$ntplot[1])) {
  cat("#### ", imgInfo$ntplot[1], " {.tabset}", "\n", sep="")
}
```

```{r Net_1, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$ntplot[1]) && any(grepl(sprintf("network.*\\(%s\\)%s.*\\.pdf$", imgInfo$ntplot[1], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("network",1, subgroup, dirInfo$image.wd, imgInfo$ntplot)
```







```{r Net-title_2, echo=FALSE, results='asis', eval=!is.na(imgInfo$ntplot[2])}
if(!is.na(imgInfo$ntplot[2])) {
  cat("#### ", imgInfo$ntplot[2], " {.tabset}", "\n", sep="")
}
```

```{r Net_2, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$ntplot[2]) && any(grepl(sprintf("network.*\\(%s\\)%s.*\\.pdf$", imgInfo$ntplot[2], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("network",2, subgroup, dirInfo$image.wd, imgInfo$ntplot)
```







```{r Net-title_3, echo=FALSE, results='asis', eval=!is.na(imgInfo$ntplot[3])}
if(!is.na(imgInfo$ntplot[3])) {
  cat("#### ", imgInfo$ntplot[3], " {.tabset}", "\n", sep="")
}
```

```{r Net_3, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$ntplot[3]) && any(grepl(sprintf("network.*\\(%s\\)%s.*\\.pdf$", imgInfo$ntplot[3], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("network",3, subgroup, dirInfo$image.wd, imgInfo$ntplot)
```







```{r Net-title_4, echo=FALSE, results='asis', eval=!is.na(imgInfo$ntplot[4])}
if(!is.na(imgInfo$ntplot[4])) {
  cat("#### ", imgInfo$ntplot[4], " {.tabset}", "\n", sep="")
}
```

```{r Net_4, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$ntplot[4]) && any(grepl(sprintf("network.*\\(%s\\)%s.*\\.pdf$", imgInfo$ntplot[4], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("network",4, subgroup, dirInfo$image.wd, imgInfo$ntplot)
```







```{r Net-title_5, echo=FALSE, results='asis', eval=!is.na(imgInfo$ntplot[5])}
if(!is.na(imgInfo$ntplot[5])) {
  cat("#### ", imgInfo$ntplot[5], " {.tabset}", "\n", sep="")
}
```

```{r Net_5, echo=FALSE,fig.align='center', message=FALSE, warning=FALSE,out.width='100%', eval=!is.na(imgInfo$ntplot[5]) && any(grepl(sprintf("network.*\\(%s\\)%s.*\\.pdf$", imgInfo$ntplot[5], ifelse(is.null(subgroup), "", paste0(".*", subgroup))), list.files(dirInfo$image.wd)))}
convert_and_include_pdf("network",5, subgroup, dirInfo$image.wd, imgInfo$ntplot)
```



