---
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE}
library(magick)
library(knitr)
library(DT)
library(magrittr)
```

```{r css-inline, echo=FALSE, results='asis'}
cat('<style>', readLines(file.path(rmd_module_dir, "styles.css")), '</style>', sep = "\n")
```

# <span class="title-text">CUMC Microbiome Core Summary Report</span>
#### <span class="author-text">  `r sprintf("%s%s",expInfo$authorName1, ifelse(is.null(expInfo$authorName2),"",paste("/",expInfo$authorName2,sep="")))`  </span>
#### <span class="date-text">`r format(Sys.Date(), '%Y-%m-%d')`</span>



***
## A.	Project name
### `r expInfo$project`

<br>

## B.	Methods
### 1.	Samples detail
-	Total number of samples: `r expInfo$samples`

### 2.	DNA extraction, Library prep and Sequencing
-	DNA Extraction positive control: `r expInfo$pos` `r expInfo$spikein`
- Extraction kit: `r expInfo$kit`
-	Sequencing method: `r expInfo$prep` `r expInfo$platform`
-	Sequencing date: `r expInfo$date`

### 3.	Analysis parameters
-	Min. sequence quality: Truncate reads truncQ = 2. It indicates all the sequences in which there was at least one read with the high probability of erroneous base assignment (>63%).
-	ASV calling: Construct an amplicon sequence variant table (ASV) table using DADA2 pipeline and assign taxonomy against Silva (99% identity).

<br>
<br>


***
## C.	Results

```{r, child = file.path(rmd_module_dir, "1_tables.Rmd")}
```

<br>

```{r, child = file.path(rmd_module_dir, "2_taxa.Rmd")}
```

<br>

```{r, child = file.path(rmd_module_dir, "3_adiv.Rmd")}
```

<br>

```{r, child = file.path(rmd_module_dir, "4_bdiv.Rmd")}
```


<br>

```{r, results='asis',echo=FALSE}
if (!is.null(imgInfo$daplot) &&  any(!is.na(imgInfo$daplot)) && length(imgInfo$daplot) >= 1) {
  cat(knitr::knit_child(
    file.path(rmd_module_dir, "5_2_DA.Rmd"),
    quiet = TRUE
  ))
}
```

<br>

```{r extra-section, results='asis', echo=FALSE}
if (!is.null(imgInfo$extra) && length(imgInfo$extra) > 0) {
  cat(knitr::knit_child(
    file.path(rmd_module_dir, "7_extra.Rmd"),
    quiet = TRUE
  ))
}
```

<br>

```{r, child = file.path(rmd_module_dir, "6_summary.Rmd")}
```

<br>

## Comment
Please leave any comments in the text box below. It will link to your email app to send an email to the Microbiome Core Bioinformatics team.

```{r, echo=FALSE, results='asis'}
# Read the external HTML file content
html_content <- readLines(file.path(rmd_module_dir, "email_form.html"), warn = FALSE)
# Replace placeholders with actual R variables
contact_email_joined <- paste(expInfo$contact_email, collapse = ",")
html_content <- gsub("\\{\\{project_name\\}\\}", expInfo$project, html_content)
html_content <- gsub("\\{\\{contact_email\\}\\}", contact_email_joined, html_content)
html_content <- gsub("\\{\\{CC_EMAIL\\}\\}", ifelse(is.null(cc_email), "", cc_email), html_content, fixed = FALSE)
# Print the modified HTML content into the R Markdown document
cat(html_content, sep = "\n")
```



***


```{r logo, echo=FALSE, out.width='50%', fig.align='center', eval=!is.null(logo_path)}
include_graphics(logo_path)
```
